Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-10-08 GWLDCII.tex
updates to figures as discussed

@@

Note that we cannot have $a_r+ 1 = j_m$ when $q$ is counterclockwise of $p_r$, since $q \not\in \Prop(j_m)$ by assumption. If the other end of $p_r$ (i.e. the end not supported on $a_r$) lies on an edge between $a_r$ and $j_m$, then since $q$ is inside $p_r$ with respect to $<_{a_r-1}$ we must have $V(q) \subseteq [a_r-1,j_m]$, and hence $q \in \cP_{m-1}$ by Lemma~\ref{lem no fourth vertex}. In particular, if $l=1$ then $p_r \in Q_{0} = \Prop(j_m)$ and we must be in this case.

If not, then there must be some propagator $p_s \in Q_{l-2}$ such that $p_r$ and $p_s$ are both supported on $I_i(p_s) := a_s$. Since $p_r$ is clockwise of $q$, and $q$ cannot be supported on $I_i(p_s)$ since $q \not\in Q_{l-1}$, it follows that $I_i(p_s) <_i I_i(p_r)$. Therefore $q$ is inside $p_s$ with respect to $<_{a_s - 1}$ as well.

\note{Sian note to self: this picture isn't right}
\begin{figure}[h]
\bas{\begin{tikzpicture}[baseline=(current bounding box.east)]
	\drawWLDfragment[9]{3}{0.3} % draw arc
	%\centerarc[linehighlight](0,0)(\zero + 3.6*\step:\zero + 5.4*\step:\radius)
	%\node[align = center] at (\zero + 4.5*\step:\radius*1.3) {\em \footnotesize 0, 1, or 2 vertices \\[3pt]\em \footnotesize in this region};
		%p_r
		\draw[smallpropagator] (\zero+2.3*\step:\radius*1.1) to [bend left = 55] (\zero + 6.7*\step:\radius*1.1); 
		\draw[smallpropagator] (\zero+2.4*\step:\radius*1.1) to [bend left = 55] (\zero + 5.3*\step:\radius*1.1); 
		\node at (\zero + 2.8*\step:\radius*0.8){\footnotesize $p_r$};
		\node at (\zero + 4.7*\step:\radius*.84){\footnotesize $q$};
	\newnode[below]{2}{a_r}
	\newnode[right]{9}{j_m}
	\node at (270:\radius*0.1) {\em all vertices of $p_r$ lie between $a_r-1$ and $j_m$};
\end{tikzpicture} \qquad \qquad \begin{tikzpicture}[baseline=(current bounding box.east)]
	\drawWLDfragment[10]{3}{0.3} % draw arc
		%random prop preventing p_s from contributing a_s-1
		\draw[smallpropagator,gray] (\zero+2.3*\step:\radius) -- (\zero + 16.5*\step:\radius) ;
		%p_s
		\draw[smallpropagator] (\zero+2.4*\step:\radius*1.1) to [bend left = 55] (\zero + 7.5*\step:\radius*1.1); 
		%p_r
		\draw[smallpropagator] (\zero+2.5*\step:\radius*1.1) to [bend left = 90] (\zero + 4.5*\step:\radius*1.1); 
		\draw[smallpropagator] (\zero+4.55*\step:\radius*1.1) to [bend left = 70] (\zero + 6.7*\step:\radius*1.1); 
		\node at (\zero + 4.5*\step:\radius*0.55){\footnotesize $p_s$};
		\node at (\zero + 3.5*\step:\radius*0.84){\footnotesize $p_r$};
		\node at (\zero + 6.2*\step:\radius*0.85){\footnotesize $q$};
	\newnode[below]{3}{a_s}
	\newnode[below]{4}{a_r}
	\newnode[below]{8}{}
	\newnode[right]{9}{j_m}
	\node at (270:\radius*0.1) {\em all vertices of $p_r$ do not lie between $a_r-1$ and $j_m$};
\end{tikzpicture} }\eas
\caption{The two cases of the induction step. Note that $I_i(p_s) <_i I_i(p_r)$}\label{fig:awkward induction step}
Now repeat the argument above with $p_s$ in place of $p_r$: if the other end of $p_s$ lands on an edge between $q$ and $j_m$ then we have $q \in \cP_{m-1}$ as above; if not then there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and $q$ on the inside of $p_t$ in the $a_t-1$ order. Therefore $I_i(p_t) <_i I_i(p_r)$
%{\color{violet} May not be necessary, but I think highlighted tex follows from "Now repeat the argument...." \begin{enumerate}\item If $V(p_r) \in [a_r-1, j_m]$ (other end closer to $j_m$) then $q$ inside $p_r$ in $a_r-1$ order. \item Else, $V(p_r) \in [i, a_r+1]$ (Maybe $[i-1, a_r +1]$?). (Main point is that other end closer to $i$) Either way,  admissibility implies that $a_s < a_r$ \item Now we repeat. Either  $V(p_s) \in [a_s-1, j_m]$ then $q$ inside $p_s$ in $a_s-1$ order \hlfix{and we are done}{not quite true; same reasoning as why we're using ``the other end of the propagator'' instead of $V(p_s) \subseteq [a_s-1, j_m]$} \item Else, $V(p_s) \in [i, a_s+1]$ (Maybe $[i-1, a_s +1]$?). Either way, admissibility implies that $a_t < a_s$ and we've already established $a_s < a_r$ \end{enumerate} We don't have to include this argument. It may be totally unnecessary. But I want to make certain that I'm not missing anything.}
Since there are finitely many steps this process can take before reaching $Q_0$, and any $p_* \in Q_0  = \Prop(j_m)$ has $j_m$ in its support by definition, this argument eventually terminates with the construction of a propagator constraining the positioning of $q$ as required. This completes the induction step, and hence the proof.\end{proof}

@@

\begin{figure}
\[
\begin{tikzpicture}[rotate = 150,baseline=(current bounding box.east),label distance = -2mm]
\begin{scope}
  \drawWLDfragment[6]{3}{0.3}
  %\drawnumbers % use this to debug
  \begin{scope}
    \clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
    \draw[smallpropagator] (\zero+2.4*\step:\radius*1.1) to [bend left = 55] (\zero + 4.6*\step:\radius*1.1); 
    \node at (\zero + 3.5*\step:\radius*0.75){\footnotesize $p$};
  \end{scope}
  \centerarc[red,line width = 2pt,line cap = round](0,0)(\zero + 2*\step:\zero+4.45*\step:\radius)
  \newbetternode[{[label distance=-3mm]above right}]{1}{n-4}
  \newbetternode[{[label distance=-3mm]above right}]{2}{n-3}
  \newbetternode[{[label distance=-3mm]above right}]{3}{n-2}
  \newbetternode[{[label distance=-3mm]above right}]{4}{n-1}
  \newnode[above]{5}{n}
  \newnode[above]{6}{1}
  \node at (180-60:\radius*0.1){\em Case 1};
\end{scope}
\end{tikzpicture}
\qquad 
\qquad 
\begin{tikzpicture}[rotate=150, baseline=(current bounding box.east)]
\begin{scope}
  \drawWLDfragment[7]{3}{0.3}
  %\drawnumbers % use this to debug
  \begin{scope}
    \clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
    \draw[smallpropagator] (\zero+1.4*\step:\radius*1.1) to [bend left = 60] (\zero + 3.5*\step:\radius*1.1); 
    \draw[smallpropagator] (\zero+3.5*\step:\radius*1.1) to [bend left = 60] (\zero + 5.6*\step:\radius*1.1); 
    \node at (\zero + 2.4*\step:\radius*0.8){\footnotesize $q$};
    \node at (\zero + 4.5*\step:\radius*0.8){\footnotesize $p$};
  \end{scope}
  \centerarc[red,line width = 2pt,line cap = round](0,0)(\zero + 1.6*\step:\zero+5.5*\step:\radius)
  \newbetternode[{[label distance=-3mm]above right}]{1}{n-5}
  \newbetternode[{[label distance=-3mm]above right}]{2}{n-4}
  \newbetternode[{[label distance=-3mm]above right}]{3}{n-3}
  \newbetternode[{[label distance=-3mm]above right}]{4}{n-2}
  \newbetternode[{[label distance=-3mm]above right}]{5}{n-1}
  \newnode[above]{6}{n}
  \newnode[above]{7}{1}
  \node at (180-60:\radius*0.1){\em Case 2};
\end{scope}
\end{tikzpicture}
\] 
  \caption{The two cases for $W$ and $p$.  No other propagators can end in the red sections.  Other segments may have additional propagators ending in them.}\label{fig special p}

@@

\begin{figure}
\[
\begin{tikzpicture}[scale = 0.85]
\node at (2.5,5.5) {\Large $V$};
\node at (12.5,5.5) {\Large $W$};
\node at (-2,2.5) {\large $n-4 \in I_1^V$};
\node at (-2,-4.5) {\large $n-4 \not\in I_1^V$};
\node at (7.5,2.5) {\Large $\longrightarrow$};
\node at (8,-4.5) {\Large $\longrightarrow$};
% n-4 \in I_1, V
\begin{scope}
\fill[pattern color = gray,pattern = north east lines] (0,4.5) -- (0,2) -- (2,2) -- (2,4.5);
\fill[pattern color = gray,pattern = north west lines] (3,4.5) -- (3,0) -- (4,0) -- (4,4.5);
\draw (0,0) grid (4,2);
\foreach \x in {0,1,2,3,4} {
  \draw (\x,2) -- (\x,4);
  \draw[smalldash] (\x,4) -- (\x,4.5);
  };
\foreach \c in {(0.5,0.5),(1.5,0.5),(1.5,1.5)} {
  \node at \c {\leplus};
}
\foreach \c in {(0.5,1.5),(2.5,1.5),(2.5,2.5),(2.5,3.3)} {
  \node at \c {\lezero};
}
\node[red] at (2.5,0.5) {\leplus};
\node at (2.5,4.2) {$\vdots$};
\begin{scope}
\fill[pattern color = gray,pattern = horizontal lines] (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (6.6,4.5) -- (4,4.5) -- (4,2);
\draw (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
\draw[smalldash] (6.5,4) -- (6.6,4.5);
\end{scope}
%\fill[color = white,path fading = south] (0,2) rectangle (6.5,4.1);
\node[below] at (0.5,0) {\scriptsize $n\vphantom{1}$};
\node[below] at (1.5,0) {\scriptsize $n-1$};
\node[below] at (2.5,0) {\scriptsize $n-2$};
\node[below] at (3.5,0) {\scriptsize $n-3$};
\node[right] at (4,0.5) {\scriptsize $n-4$};
\node[right] at (4,1.5) {\scriptsize $n-5$};
\end{scope}

% n-4 \in I_1, W
\begin{scope}[shift = {(9,0)}]
\fill[pattern color = gray,pattern = north east lines] (0,4.5) -- (0,2) -- (2,2) -- (2,4.5);
\fill[pattern color = gray,pattern = north west lines] (2,4.5) -- (2,0) -- (3,0) -- (3,4.5);
\draw (0,-1) grid (3,2);
\foreach \x in {0,1,2,3} {
  \draw (\x,2) -- (\x,4);
  \draw[smalldash] (\x,4) -- (\x,4.5);
  };
\foreach \c in {(0.5,0.5),(1.5,0.5),(1.5,1.5)} {
  \node at \c {\leplus};
}
\node[red] at (0.5,1.5) {\leplus};
\foreach \c in {(0.5,-0.5),(1.5,-0.5),(2.5,-0.5)} {
  \node[blue] at \c {\leplus};
}
\begin{scope}[shift = {(-1,0)}]
\fill[pattern color = gray,pattern = horizontal lines] (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (6.6,4.5) -- (4,4.5) -- (4,2);
\draw (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
\draw[smalldash] (6.5,4) -- (6.6,4.5);
\end{scope}
\node[below] at (0.5,-1) {\scriptsize $n\vphantom{1}$};
\node[below] at (1.5,-1) {\scriptsize $n-1$};
\node[below] at (2.5,-1) {\scriptsize $n-2$};
\node[right] at (3,-0.5) {\scriptsize $n-3$};
\node[right] at (3,0.5) {\scriptsize $n-4$};
\node[right] at (3,1.5) {\scriptsize $n-5$};
\end{scope}

% n-4 \not\in I_1, V
\begin{scope}[shift = {(0,-6)}]
\fill[pattern color = gray,pattern = north east lines] (0,3.5) -- (0,1) -- (2,1) -- (2,3.5);
\fill[pattern color = gray,pattern = north west lines] (3,3.5) -- (3,0) -- (4,0) -- (4,3.5);
\draw (0,0) grid (4,1);
\foreach \x in {0,1,2,3,4} {
  \draw (\x,1) -- (\x,3);
    \draw[smalldash] (\x,3) -- (\x,3.5);
  };
\foreach \c in {(0.5,0.5),(1.5,0.5),(2.5,1.5),(2.5,2.3)} {
  \node at \c {\lezero};
}
\node[red] at (2.5,0.5) {\leplus};
\node at (2.5,3.2) {$\vdots$};
\begin{scope}[shift = {(1,-1)}]
\fill[pattern color = gray,pattern = horizontal lines] (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4)-- (6.6,4.5) -- (3,4.5) -- (3,1);
\draw (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
\draw[smalldash] (6.5,4) -- (6.6,4.5);
\end{scope}

@@

% n-4 \not\in I_1, W
\begin{scope}[shift = {(9,-6)}]
\fill[pattern color = gray,pattern = north east lines] (0,3.5) -- (0,1) -- (2,1) -- (2,3.5);
\fill[pattern color = gray,pattern = north west lines] (2,3.5) -- (2,0) -- (3,0) -- (3,3.5);
\draw (0,-1) grid (3,1);
\foreach \x in {0,1,2,3} {
  \draw (\x,1) -- (\x,3);
  \draw[smalldash] (\x,3) -- (\x,3.5);
  };
\node at (0.5,0.5) {\lezero};
\node[red] at (1.5,0.5) {\leplus};
\foreach \c in {(0.5,-0.5),(1.5,-0.5),(2.5,-0.5)} {
  \node[blue] at \c {\leplus};
}
\begin{scope}[shift = {(0,-1)}]
\fill[pattern color = gray,pattern = horizontal lines] (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4)-- (6.6,4.5) -- (3,4.5) -- (3,1);
\draw (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
\draw[smalldash] (6.5,4) -- (6.6,4.5);
\end{scope}
\node[below] at (0.5,-1) {\scriptsize $n\vphantom{1}$};
\node[below] at (1.5,-1) {\scriptsize $n-1$};
\node[below] at (2.5,-1) {\scriptsize $n-2$};
\node at (3.5,-0.7) {\scriptsize $n-3$};
\node at (3.7,-0.2) {\scriptsize $n-4$};
\node[right] at (4,0.5) {\scriptsize $n-5$};
\end{scope}
\end{tikzpicture}
\]
\caption{The Le diagrams for $V$ and $W$ in the setting of Theorem~\ref{thm dim}. The shaded regions indicate where the plusses match up perfectly from $V$ to $W$, the red plusses exist if and only if $n-2 \in I_{n-2}^V$, and the blue plusses are the three new plusses coming from the induction step.}\label{fig:le diagrams bijection}
\end{figure}

>>>>

\newcommand{\leplusbold}[1][black]{%
  \tikz\draw[#1,line width=1.5pt,scale = 0.35,line cap = round] (0,0) -- (1,0)(0.5,0.5) -- (0.5,-0.5);
}

@@

Note that we cannot have $a_r+ 1 = j_m$ when $q$ is counterclockwise of $p_r$, since $q \not\in \Prop(j_m)$ by assumption. If the other end of $p_r$ (i.e. the end not supported on $a_r$) lies on an edge between $a_r$ and $j_m$, then since $q$ is inside $p_r$ with respect to $<_{a_r-1}$ we must have $V(q) \subseteq [a_r-1,j_m]$, and hence $q \in \cP_{m-1}$ by Lemma~\ref{lem no fourth vertex}; this is illustrated in Figure~\ref{fig gn proof induction 1}. In particular, if $l=1$ then $p_r \in Q_{0} = \Prop(j_m)$ and we must be in this case.

If not, then there must be some propagator $p_s \in Q_{l-2}$ such that $p_r$ and $p_s$ are both supported on $I_i(p_s) := a_s$; see Figure~\ref{fig gn proof induction 2}. Since $p_r$ is clockwise of $q$, and $q$ cannot be supported on $I_i(p_s)$ since $q \not\in Q_{l-1}$, it follows that $I_i(p_s) <_i I_i(p_r)$. Therefore $q$ is inside $p_s$ with respect to $<_{a_s - 1}$ as well.

\begin{figure}
\[
\begin{tikzpicture}[baseline=(current bounding box.east)]
  \begin{scope}
  \drawWLDfragment[10]{4}{0.4} 
  %\drawnumberspartial % use this to debug
  \centerarc[linehighlight](0,0)(\zero + 2.6*\step:\zero + 3.9*\step:\radius)
  \newnode{1}{i}
  \newnode[right]{10}{j_m}
  \begin{scope}
\clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
\newpropbend{3}{8.5}{50}
\newpropbend{3.3}{7}{40}
\end{scope}
\node at (\zero+5*\step:\radius*0.46) {\scriptsize $p_r$};
\node at (\zero + 6*\step:\radius*0.75) {\scriptsize $q$};
\node at (\zero + 3.2*\step:\radius*1.1) {\scriptsize $a_r$};
\end{scope}
\end{tikzpicture}
\]
\caption{If $q$ is counterclockwise of $p_r$ and the other end of $p_r$ lies on an edge between $a_r$ and $j_m$, then $V(q) \subseteq [a_{r-1},j_m]$. The vertex $a_r$ lies somewhere within the (blue) highlighted region.}\label{fig gn proof induction 1}
\end{figure}

\begin{figure}
\[
\begin{tikzpicture}[baseline=(current bounding box.east)]
  \begin{scope}
  \drawWLDfragment[10]{4}{0.3} 
  %\drawnumberspartial % use this to debug
  \centerarc[linehighlight](0,0)(\zero + 4.5*\step:\zero + 5.3*\step:\radius)
  \newnode{1}{i}
  \newnode[below]{6}{a_r}
  \newnode[right]{10}{j_m}
  \begin{scope}
\clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
\clip (\zero + 5.5*\step:\radius*1.5) circle (\radius*0.85);
\newpropbend{5}{18}{30} %p_s
\newpropbend{5.5}{15}{30} %p_r
\newpropbend{6}{12}{30} %q
\end{scope}
\node at (\zero+5.7*\step:\radius*0.72) {\scriptsize $p_r$};
\node at (\zero+4.15*\step:\radius*0.71) {\scriptsize $p_s$};
\node at (\zero + 6.8*\step:\radius*0.83) {\scriptsize $q$};
\node at (\zero + 5*\step:\radius*1.07) {\scriptsize $a_s$};
\end{scope}
\end{tikzpicture}
\qquad \qquad
\begin{tikzpicture}[baseline=(current bounding box.east)]
  \begin{scope}
  \drawWLDfragment[10]{4}{0.3} 
  %\drawnumberspartial % use this to debug
  \centerarc[linehighlight](0,0)(\zero + 2.5*\step:\zero + 3.7*\step:\radius)
  \centerarc[linehighlight](0,0)(\zero + 6.3*\step:\zero + 7.5*\step:\radius)
  \newnode{1}{i}
  \newnode[right]{10}{j_m}
  \begin{scope}
\clipcenterarc(0,0)(\startpoint:\endpoint-\step:\radius)
%\clip (\zero + 5.5*\step:\radius*1.5) circle (\radius*0.85);
\newpropbend{2.9}{15}{30} %p_s
\newpropbend{3}{6.8}{45} %p_r
\newpropbend{7}{15}{30} %q
\end{scope}
\node at (\zero+5.3*\step:\radius*0.78) {\scriptsize $p_r$};
\node at (\zero+2.3*\step:\radius*0.8) {\scriptsize $p_s$};
\node at (\zero + 7.4*\step:\radius*0.8) {\scriptsize $q$};
\node at (\zero + 3*\step:\radius*1.07) {\scriptsize $a_s$};
\node at (\zero + 7*\step:\radius*1.07) {\scriptsize $a_r$};
\end{scope}
\end{tikzpicture}
\]
\caption{If the other end of $p_r$ does not lie on an edge between $a_r$ and $j_m$, then we must have a propagator $p_s \in Q_{l-2}$ in one of the depicted configurations. The (blue) highlighted regions indicate the approximate position of a vertex whose precise position is unknown. Cut-off propagators indicate that the location of the propagator's other end is unknown; in particular, no meaning should be ascribed to the angle at which these propagators are drawn.}\label{fig gn proof induction 2}
\end{figure}
Now repeat the argument above with $p_s$ in place of $p_r$: if the other end of $p_s$ lands on an edge between $q$ and $j_m$ then we have $q \in \cP_{m-1}$ as above; if not then there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and $q$ on the inside of $p_t$ in the $a_t-1$ order. Therefore $I_i(p_t) <_i I_i(p_r)$
%{\color{violet} May not be necessary, but I think highlighted tex follows from "Now repeat the argument...." \begin{enumerate}\item If $V(p_r) \in [a_r-1, j_m]$ (other end closer to $j_m$) then $q$ inside $p_r$ in $a_r-1$ order. \item Else, $V(p_r) \in [i, a_r+1]$ (Maybe $[i-1, a_r +1]$?). (Main point is that other end closer to $i$) Either way,  admissibility implies that $a_s < a_r$ \item Now we repeat. Either  $V(p_s) \in [a_s-1, j_m]$ then $q$ inside $p_s$ in $a_s-1$ order \hlfix{and we are done}{not quite true; same reasoning as why we're using ``the other end of the propagator'' instead of $V(p_s) \subseteq [a_s-1, j_m]$} \item Else, $V(p_s) \in [i, a_s+1]$ (Maybe $[i-1, a_s +1]$?). Either way, admissibility implies that $a_t < a_s$ and we've already established $a_s < a_r$ \end{enumerate} We don't have to include this argument. It may be totally unnecessary. But I want to make certain that I'm not missing anything.}
Since there are finitely many steps this process can take before reaching $Q_0$, and any $p_* \in Q_0  = \Prop(j_m)$ has $j_m$ in its support by definition, this argument eventually terminates with the construction of a propagator constraining the positioning of $q$ as required. This completes the induction step, and hence the proof.\end{proof}

@@

\begin{figure}
\[
\begin{tikzpicture}[rotate = 150,baseline=(current bounding box.east),label distance = -2mm]
\begin{scope}
  \drawWLDfragment[6]{3}{0.3}
  %\drawnumbers % use this to debug
  \begin{scope}
    \clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
    \draw[smallpropagator] (\zero+2.4*\step:\radius*1.1) to [bend left = 55] (\zero + 4.6*\step:\radius*1.1); 
    \node at (\zero + 3.5*\step:\radius*0.75){\footnotesize $p$};
  \end{scope}
  \centerarc[red,line width = 2pt,line cap = round](0,0)(\zero + 2*\step:\zero+4.45*\step:\radius)
  \newbetternode[{[label distance=-3mm]above right}]{1}{n-4}
  \newbetternode[{[label distance=-3mm]above right}]{2}{n-3}
  \newbetternode[{[label distance=-3mm]above right}]{3}{n-2}
  \newbetternode[{[label distance=-3mm]above right}]{4}{n-1}
  \newnode[above]{5}{n}
  \newnode[above]{6}{1}
  \node at (180-60:\radius*0.1){\em Case 1};
\end{scope}
\end{tikzpicture}
\qquad 
\qquad 
\begin{tikzpicture}[rotate=150, baseline=(current bounding box.east)]
\begin{scope}
  \drawWLDfragment[7]{3}{0.3}
  %\drawnumbers % use this to debug
  \begin{scope}
    \clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
    \draw[smallpropagator] (\zero+1.4*\step:\radius*1.1) to [bend left = 60] (\zero + 3.5*\step:\radius*1.1); 
    \draw[smallpropagator] (\zero+3.5*\step:\radius*1.1) to [bend left = 60] (\zero + 5.6*\step:\radius*1.1); 
    \node at (\zero + 2.4*\step:\radius*0.8){\footnotesize $q$};
    \node at (\zero + 4.5*\step:\radius*0.8){\footnotesize $p$};
  \end{scope}
  \centerarc[red,line width = 2pt,line cap = round](0,0)(\zero + 1.6*\step:\zero+5.5*\step:\radius)
  \newbetternode[{[label distance=-3mm]above right}]{1}{n-5}
  \newbetternode[{[label distance=-3mm]above right}]{2}{n-4}
  \newbetternode[{[label distance=-3mm]above right}]{3}{n-3}
  \newbetternode[{[label distance=-3mm]above right}]{4}{n-2}
  \newbetternode[{[label distance=-3mm]above right}]{5}{n-1}
  \newnode[above]{6}{n}
  \newnode[above]{7}{1}
  \node at (180-60:\radius*0.1){\em Case 2};
\end{scope}
\end{tikzpicture}
\] 
  \caption{The two cases for $W$ and $p$.  No other propagators can end in the bolded (red) sections.  Other segments may have additional propagators ending in them.}\label{fig special p}

@@

\begin{figure}
\[
\begin{tikzpicture}[scale = 0.85]
\node at (2.5,5.5) {\Large $V$};
\node at (12.5,5.5) {\Large $W$};
\node at (-2,2.5) {\large $n-4 \in I_1^V$};
\node at (-2,-4.5) {\large $n-4 \not\in I_1^V$};
\node at (7.5,2.5) {\Large $\longrightarrow$};
\node at (8,-4.5) {\Large $\longrightarrow$};
% n-4 \in I_1, V
\begin{scope}
\fill[pattern color = gray,pattern = north east lines] (0,4.5) -- (0,2) -- (2,2) -- (2,4.5);
\fill[pattern color = gray,pattern = north west lines] (3,4.5) -- (3,0) -- (4,0) -- (4,4.5);
\draw (0,0) grid (4,2);
\foreach \x in {0,1,2,3,4} {
  \draw (\x,2) -- (\x,4);
  \draw[smalldash] (\x,4) -- (\x,4.5);
  };
\foreach \c in {(0.5,0.5),(1.5,0.5),(1.5,1.5)} {
  \node at \c {\leplus};
}
\foreach \c in {(0.5,1.5),(2.5,1.5),(2.5,2.5),(2.5,3.3)} {
  \node at \c {\lezero};
}
\node[red] at (2.5,0.5) {\leplusbold[red]};
\node at (2.5,4.2) {$\vdots$};
\begin{scope}
\fill[pattern color = gray,pattern = horizontal lines] (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (6.6,4.5) -- (4,4.5) -- (4,2);
\draw (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
\draw[smalldash] (6.5,4) -- (6.6,4.5);
\end{scope}
%\fill[color = white,path fading = south] (0,2) rectangle (6.5,4.1);
\node[below] at (0.5,0) {\scriptsize $n\vphantom{1}$};
\node[below] at (1.5,0) {\scriptsize $n-1$};
\node[below] at (2.5,0) {\scriptsize $n-2$};
\node[below] at (3.5,0) {\scriptsize $n-3$};
\node[right] at (4,0.5) {\scriptsize $n-4$};
\node[right] at (4,1.5) {\scriptsize $n-5$};
\end{scope}

% n-4 \in I_1, W
\begin{scope}[shift = {(9,0)}]
\fill[pattern color = gray,pattern = north east lines] (0,4.5) -- (0,2) -- (2,2) -- (2,4.5);
\fill[pattern color = gray,pattern = north west lines] (2,4.5) -- (2,0) -- (3,0) -- (3,4.5);
\draw (0,-1) grid (3,2);
\foreach \x in {0,1,2,3} {
  \draw (\x,2) -- (\x,4);
  \draw[smalldash] (\x,4) -- (\x,4.5);
  };
\foreach \c in {(0.5,0.5),(1.5,0.5),(1.5,1.5)} {
  \node at \c {\leplus};
}
\node[red] at (0.5,1.5) {\leplusbold[red]};
\foreach \c in {(0.5,-0.5),(1.5,-0.5),(2.5,-0.5)} {
  \node[blue] at \c {\leplus};
}
\begin{scope}[shift = {(-1,0)}]
\fill[pattern color = gray,pattern = horizontal lines] (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (6.6,4.5) -- (4,4.5) -- (4,2);
\draw (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
\draw[smalldash] (6.5,4) -- (6.6,4.5);
\end{scope}
\node[below] at (0.5,-1) {\scriptsize $n\vphantom{1}$};
\node[below] at (1.5,-1) {\scriptsize $n-1$};
\node[below] at (2.5,-1) {\scriptsize $n-2$};
\node[right] at (3,-0.5) {\scriptsize $n-3$};
\node[right] at (3,0.5) {\scriptsize $n-4$};
\node[right] at (3,1.5) {\scriptsize $n-5$};
\end{scope}

% n-4 \not\in I_1, V
\begin{scope}[shift = {(0,-6)}]
\fill[pattern color = gray,pattern = north east lines] (0,3.5) -- (0,1) -- (2,1) -- (2,3.5);
\fill[pattern color = gray,pattern = north west lines] (3,3.5) -- (3,0) -- (4,0) -- (4,3.5);
\draw (0,0) grid (4,1);
\foreach \x in {0,1,2,3,4} {
  \draw (\x,1) -- (\x,3);
    \draw[smalldash] (\x,3) -- (\x,3.5);
  };
\foreach \c in {(0.5,0.5),(1.5,0.5),(2.5,1.5),(2.5,2.3)} {
  \node at \c {\lezero};
}
\node[red] at (2.5,0.5) {\leplusbold[red]};
\node at (2.5,3.2) {$\vdots$};
\begin{scope}[shift = {(1,-1)}]
\fill[pattern color = gray,pattern = horizontal lines] (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4)-- (6.6,4.5) -- (3,4.5) -- (3,1);
\draw (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
\draw[smalldash] (6.5,4) -- (6.6,4.5);
\end{scope}

@@

% n-4 \not\in I_1, W
\begin{scope}[shift = {(9,-6)}]
\fill[pattern color = gray,pattern = north east lines] (0,3.5) -- (0,1) -- (2,1) -- (2,3.5);
\fill[pattern color = gray,pattern = north west lines] (2,3.5) -- (2,0) -- (3,0) -- (3,3.5);
\draw (0,-1) grid (3,1);
\foreach \x in {0,1,2,3} {
  \draw (\x,1) -- (\x,3);
  \draw[smalldash] (\x,3) -- (\x,3.5);
  };
\node at (0.5,0.5) {\lezero};
\node[red] at (1.5,0.5) {\leplusbold[red]};
\foreach \c in {(0.5,-0.5),(1.5,-0.5),(2.5,-0.5)} {
  \node[blue] at \c {\leplus};
}
\begin{scope}[shift = {(0,-1)}]
\fill[pattern color = gray,pattern = horizontal lines] (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4)-- (6.6,4.5) -- (3,4.5) -- (3,1);
\draw (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
\draw[smalldash] (6.5,4) -- (6.6,4.5);
\end{scope}
\node[below] at (0.5,-1) {\scriptsize $n\vphantom{1}$};
\node[below] at (1.5,-1) {\scriptsize $n-1$};
\node[below] at (2.5,-1) {\scriptsize $n-2$};
\node at (3.5,-0.7) {\scriptsize $n-3$};
\node at (3.7,-0.2) {\scriptsize $n-4$};
\node[right] at (4,0.5) {\scriptsize $n-5$};
\end{scope}
\end{tikzpicture}
\]
\caption{The Le diagrams for $V$ and $W$ in the setting of Theorem~\ref{thm dim}. The shaded regions indicate where the plusses match up perfectly from $V$ to $W$, the bold (red) plusses exist if and only if $n-2 \in I_{n-2}^V$, and the (blue) plusses in the bottom row of the $W$ diagrams are the three new plusses coming from the induction step.}\label{fig:le diagrams bijection}
\end{figure}
